Pillar 1 - Sequential Pattern Mining

### 2019-01-31 Pillar 1 - Sequential Pattern Mining.Rmd

#
# Making transactions
transactions                  <- make_transaction(item = item   )
transactions_PF               <- make_transaction(item = item_PF)
transactions_HL               <- make_transaction(item = item_HL)
transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)

transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)

@@

#
# Making sequences
sequences          <- make_sequence(item = item   )
sequences_PF       <- make_sequence(item = item_PF)
sequences_HL       <- make_sequence(item = item_HL)

sequences_expanded     <- make_sequence(data = d_transactions_expanded, item = item)
sequences_expanded_PF  <- make_sequence(data = d_transactions_expanded, item = item_PF)
sequences_expanded_HL  <- make_sequence(data = d_transactions_expanded, item = item_HL)

@@

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)

@@

### CSPADE Algorithm
##TODO:paste item: e.g."COR1002_8"

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL,
   n_students,
   SR_taken, SR_PF, SR_HL,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)

>>>>

#
# Making transactions
transactions                  <- make_transaction(item = item   )
transactions_PF               <- make_transaction(item = item_PF)
transactions_HL               <- make_transaction(item = item_HL)
transactions_Grade            <- make_transaction(item = item_Grade)
transactions_Taken            <- make_transaction(data = d_transactions_not_taken, item = item_taken)

transactions_expanded         <- make_transaction(data = d_transactions_expanded, item = item)
transactions_expanded_PF      <- make_transaction(data = d_transactions_expanded, item = item_PF)
transactions_expanded_HL      <- make_transaction(data = d_transactions_expanded, item = item_HL)
transactions_expanded_Grade   <- make_transaction(data = d_transactions_expanded, item = item_Grade)

@@

#
# Making sequences
sequences          <- make_sequence(item = item   )
sequences_PF       <- make_sequence(item = item_PF)
sequences_HL       <- make_sequence(item = item_HL)
sequences_Grade    <- make_sequence(item = item_Grade)

sequences_expanded        <- make_sequence(data = d_transactions_expanded, item = item)
sequences_expanded_PF     <- make_sequence(data = d_transactions_expanded, item = item_PF)
sequences_expanded_HL     <- make_sequence(data = d_transactions_expanded, item = item_HL)
sequences_expanded_Grade  <- make_sequence(data = d_transactions_expanded, item = item_Grade)

@@

rm(clean_AR, my_apriori,
   transactions, transactions_PF, transactions_HL, transactions_Grade,
   course_id_fail, course_id_low,
   AR_taken, AR_PF, AR_HL, AR_not_taken, AR_expanded_taken, AR_expanded_PF, AR_expanded_HL)

@@

### CSPADE Algorithm
##TODO: add AR_grade, SR_grade

@@

#clean unnecessary objects
rm(clean_SR, my_SR, 
   sequences, sequences_PF, sequences_HL, sequences_Grade,
   sequences_expanded, sequences_expanded_PF, sequences_expanded_HL, sequences_expanded_Grade,
   n_students,
   SR_taken, SR_PF, SR_HL,
   SR_expanded_taken, SR_expanded_PF, SR_expanded_HL)
